\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-15 paper/figures.tex
add applications table

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 Entropy}---%
        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
        In each address observed, we counted the number of bits set, and compared this to
        randomly generated addresses. If the 96 non-network bits
        of each address were chosen randomly, we would expect to see a Binomial distribution
        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
        bits set, suggesting that censors might be able to distinguish between phantom host addresses
        and legitimate ones.\looseness=-1
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym.\ routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered phantom host addresses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.
    }
    \label{fig:implementation}
\end{figure}
}

>>>>

\newcommand{\FigIpEntropy}{
\begin{figure}[t]
    \centering
    %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
    \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
    \caption{\textbf{IPv6 Entropy}---%,
        Censors may be able to distinguish random-looking phantom host IPv6 addresses
        from legitimately used ones based on the address's entropy.
        We used the Entropy/IP tool~\cite{foremski2016entropy} to analyze the entropy
        of 4013 IPv6 addresses observed by our tap. This plot from the tool shows the
        normalized entropy of each nibble in the addresses, which is fairly high
        for most of the non-network prefix nibbles. In total, these addresses have
        about 75~bits of entropy (out of 96 expected), and the relatively high entropy
        present in each nibble would make it difficult for a censor to block without
        significant false positives / negatives. While distinguishable from random
        given enough samples,
        we can also use the Entropy/IP tool to generate addresses from the Bayesian Network
        model it produces.}
    \label{fig:ipentropy}
\end{figure}
}

\newcommand{\FigIpBits}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
    \caption{\textbf{IPv6 bits set}---%
        We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
        and observed by our tap,
        and compare it to the Binomial distribution (Random) we would expect to see
        if the 96 non-network bits of each address were chosen randomly. In practice,
        we observe much fewer bits set.
        Nonetheless, the significant overlap of these distributions
        would make it difficult for censors to block any individual phantom hosts
        without collateral risk of blocking legitimate services.
       % suggesting that censors might be able to distinguish between phantom host addresses
        % and legitimate ones.
        %We note there are several /64 subnets that had many
        %addresses that appeared random (visibly overlapping the random distribution).
    }
    \label{fig:ipbits}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym.\ routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %ISP Deployment           &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}

\newcommand{\TabApplications}{
\begin{table}[t]
    \centering
    \begin{tabular}{l|ccccc}
            & \rot{OSSH~\cite{ossh}} &
              \rot{\texttt{obfs4}~\cite{obfs4}} &
              \rot{Mask Sites} &
              \rot{TLS eSNI} & \rot{WebRTC} \\
            \hline
            Active probe resistant  & \no  & \yes & \yes & \yes & \yes \\
            Randomized or Tunneling & R    & R    & T    &  T   & T \\
            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
    \end{tabular}
    \caption{\textbf{\scheme Applications}\,---\,
    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
        ones attempt to have no discernable protocol fingerprint or headers.
        For existing protocols, we list any known attacks suggested in the literature that let censors
        passively detect them. We also list if we have implemented the application in our prototype.}
    \label{tab:applications}
\end{table}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered phantom host addresses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.}
    \label{fig:implementation}
\end{figure}
}
